\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-07 pldi/draft.tex
Edit the web-index use case part of the paper

\heading{Program}
At a high level, the pipeline is comprised of two distinct components that coarsely correspond to a front- and a back-end communicating via \unix pipes.
The front-end downloads pages and extracts their URLs from their source, feeding back \todo{to} the start of the pipeline;
  the back-end applies natural-language processing---\eg trigrams, character conversion, term frequencies---to index the incoming pages.
The pipeline contains a total of 52 stages (18 for the font-end and 34 for the back-end), with written in multiple languages---for example, its \ttt{url-extract}ion utility is written in JavaScript whereas its \ttt{word-stem}ming utility is in Python.
\sys can still operate on them as their parallelizability properties---\sta for \ttt{url-extract} and \ttt{word-stem}---can be described by its DSL.

\heading{Results}
To simplify execution (and avoid hitting Wikipedia), we have saved a recent version of Wikipedia to a server within the network and to redirect all \ttt{curl} requests there.
The complexity of this pipeline makes end-to-end measurements difficult, so we measure the improvements on the three components individually and then report the differences

@@

>>>>

\heading{Program} At a high level, the pipeline is comprised of two
distinct components that coarsely correspond to a front- and a
back-end communicating via \unix pipes.  The front-end downloads pages
and extracts their URLs from their source, feeding back \todo{to} the
start of the pipeline; the back-end extracts the text from the html
pages and then applies natural-language processing---\eg trigrams,
character conversion, term frequencies---to index the incoming pages.
The pipeline contains a total of 52 stages (18 for the font-end and 34
for the back-end) written in multiple languages---for example,
its \ttt{url-extract}ion utility is written in JavaScript whereas its
\ttt{word-stem}ming utility is in Python.  \sys can still operate on
them as their parallelizability properties---\sta for
\ttt{url-extract} and \ttt{word-stem}---can be described by its DSL.

\heading{Results} To simplify execution (and avoid hitting Wikipedia),
we have saved a recent version of Wikipedia to a server within the
network and to redirect all \ttt{curl} requests there.  The complexity
of this pipeline makes end-to-end measurements difficult, so we
measure the improvements on the two components components individually
and then report the differences. With parallelism set to \todo{2/16}
the execution time achieved by \sys is \todo{X} for the front-end and
\todo{Y} for the back-end, while the original execution time is
\todo{X} for the front-end and \todo{Y'} for the back-end. \kk{If the
  front-end takes a lot of time (compared to the back-end), we might
  better not report it with the premise that it is a feedback cycle
  that cannot be parallelized by \sys.}

@@

Since the front-end contains a feedback cycle, \sys \todo{doesn't
  parallelize it}, and in both cases it takes \todo{X seconds} to
complete. However, \sys parallelizes the back-end and achieves a
speedup of \todo{X} with parallelism set to \todo{2/16}. Several
stages of the pipeline are \sta (such as the \ttt{word-stem} script
and the text extraction) and that allows \sys to achieve benefits by
exposing data parallelism. Note that the back-end part of the script
contains 34 stages executing in parallel, so the sequential version
\todo{already benefits from task-based parallelism} \kk{not totally
  true}.
